Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-08-06 tex/sections/intro.tex
Fix some readability issues in Chapter 1
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Although a fully decentralized blockchain based on the participation of every user looks appealing, it is not as perfect
as it might seem. A blockchain consensus protocol relies on a network of computers, not humans. Ordinary users use
simple and similar computer systems. That means, they all have similar vulnerabilities which could be used by an
adversary to catastrophically attack the consensus protocol. For example, if a malware, probably using a common zero-day
vulnerability, has the ability to infect a large portion of normal personal computers, it could be used by an
adversary to control the majority of participants in the consensus protocol and compromise the security of the
blockchain.

@@

Centralized block generation brings some interesting features to the Argennon platform, such as off
chain fee payment, optimistic instant transaction confirmation and runoff protection. However, it also increases
the possibility of transaction censorship. In Argennon, this problem is addressed by a special
High Priority Transaction (HPT) protocol.

Each block of the Argennon blockchain contains a set of Computational Integrity (CI) statements and a commitment to
the corresponding ledger state of the block. The CI set defines how
the ledger state of the block can be reached from the state of its previous block via a set of intermediate states.
Each individual CI statement defines an ordered list of external requests\footnote{External requests in Argennon are
similar to transactions in older blockchains.} and determines the intermediate states before and after executing those
requests:
\[
    \tau_{(s_i,s_{i+1},\mathbb{R})} \coloneqq \text{``$s_{i+1}$ is the next state after executing external requests
        $\mathbb{R}$ on state $s_i$''}
\]
Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
of these CI statements (STARK/SNARK) from the Argennon cloud. They can also receive the state of the previous
block (the required part of it) and proofs that show the received data is consistent with the previous block commitment.

@@

Argennon applications (i.e smart contracts) are stored in a high level text based language on the blockchain. This
language is intended for preserving the
high level information of the application logic to facilitate platform specific compiler optimization at a host
machine. This enables delegates to compile and optimize Argennon applications for their specific hardware platforms
and execute applications efficiently.

>>>>

Although a fully decentralized blockchain based on the participation of every user looks appealing, it is not as perfect
as it might seem. A blockchain consensus protocol relies on a network of computers, not humans. Ordinary users use
simple and similar computer systems. That means, they all have similar vulnerabilities and weaknesses which could be
used by an adversary to catastrophically attack the consensus protocol. For example, if a malware, probably using a
common zero-day
vulnerability, has the ability to infect a large portion of normal personal computers, it could be used by an
adversary to control the majority of participants in the consensus protocol and compromise the security of the
blockchain.

@@

Centralized block generation brings some interesting features to the Argennon platform, such as flexible and lower
fees, off chain fee payment, optimistic instant transaction confirmation, and runoff protection.
However, it also increases the possibility of transaction censorship. In Argennon, this problem is addressed by a
special High Priority Transaction (HPT) protocol.

Each block of the Argennon blockchain contains a set of Computational Integrity (CI) statements and a commitment to
the final ledger state of the block. The CI set defines how the final ledger state of the block can be reached from
the state of its previous block via a set of intermediate states.
Each individual CI statement defines an ordered list of external requests\footnote{External requests in Argennon are
similar to transactions in older blockchains.} and determines the intermediate states before and after executing those
requests:
\[
    \tau_{(s_i,s_{i+1},\mathbb{R})} \coloneqq \text{``$s_{i+1}$ is the next state after executing external requests
        $\mathbb{R}$ on state $s_i$''}
\]
Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
of these CI statements (STARK/SNARK) from the Argennon cloud. They can also receive the state of the previous
block (the required part of it) and proofs that show the received data is consistent with the previous block commitment.

@@

Argennon applications (i.e smart contracts) are stored in a high level text based language on the blockchain. This
language is intended for preserving the
high level information of the application logic to facilitate platform specific compiler optimization at a host
machine. This enables delegates to compile and optimize Argennon applications for their specific hardware platforms
and execute applications efficiently, ensuring the state transition can be found as fast as possible.
